\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-17 paper.tex
Revise up to figs. 11 and table 1.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/grinJD31}
  \caption{(a) Etching rate $v$ and (b) porosity $p$ as a function of the
    density current $j_\perp$, obtained from Fig. \ref{fig:JDR}. We
    show the data points and the results of power
    law fits, yielding $v=0.53j_\perp^{0.79}$ and
    $p=0.3j_\perp^0.24$, with corresponding correlation coefficients
      $r_v^2=0.993$ and $r_p^2=0.989$ (here $v$ is in nm/s, $p$ is
      dimensionless and $j_\perp$ is in mA/cm$^2$). \notaL{cambia J por $j_\perp$, V por $v$ y P
      por $p$. Quita el letrero fitting data, la ecuación y el valor
      de $R^2$}\notaL{Los ajustes ¿son correctos con estas unidades?}}
  \label{fig:Indr1}
\end{figure}
By relating among themselves the panels of Fig. \ref{fig:JDR} we
may obtain the etching rate $v$ and the porosity $p$ as
functions of the current density $j_\perp$. The results are shown in
Fig. \ref{fig:Indr1}.\notaL{\ldots Apenas aquí dijiste cuál fue el
  tiempo de ataque de la muestra dos: relating to depth and time ($
  200 \ \ s $ ). ¿Es correcto este tiempo? Ponlo en su lugar}
We fitted the data points with simple power laws and found
$v=0.53j_\perp^{0.79}$ and $p=0.3j_\perp^{0.24}$, where $v$ is
expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.993$
and $r_p^2=0.989$. \notaL{Digresión teórica. El producto $pv$ es
  proporcional a la cantidad de materia removida por segundo. En mi
  opinión, esto debería ser proporcional a la corriente $pv\propto
  j_\perp$. ¿Es correcto? A tí te sale algo parecido pero no
  exacto. ¿Se podrá hacer un mejor ajuste tomando esto en cuenta?
  ¿Alguien lo ha discutido en la literatura?}\notaL{En todo caso, todo
  esto se tiene que rehacer usando la expresión teórica correcta y las
  posiciones correctas}

@@

\subsection{GRIN Porous Silicon Microcavities}
\label{sec:grin-porous-silicon}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Images/MicrGrin}
	\caption{Diagram of a microcavity of porous silicon
            GRIN. Alternate layers are obtained of high (H) refractive
            index $n_{Hi}$ and low (L) refractive index
            $n_{Li}$, where $N_H$ is the number of layers for
            $n_{Hi}$ and $N_L$ is the number of layers for
            $n_{Li}$. Then,  $d_{Hi}$ is the monolayer thickness
            of  $n_{Hi}$ at that measurement point and $d_{Li}$
            is the monolayer thickness of $n_{Hi}$ at that
            measurement point. Therefore,  $d_i$ is the total
            thickness calculated for each of the measurements,
            defining a i = $ A, B, C$. Having the following
            relationship $d_i =(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
            (2d_{Hi})$. }
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
gradient for monolayers should be shown in section 4.2, where we
designed an electolytic cell suitable for our experiments and giving
us the expected results of the simulation in section 4.1. Now our
purpose is to manufacture more complex photonic structures such as the
Porous silicon microcavities GRIN, taking into account that we start
from having a tip electrode almost on the surface and by making a
variation of currents we can achieve the effect of alternating the
layers. Alternate layers are obtained of high (H) refractive index
$n_{Hi}$ and low (L) refractive index $n_{Li}$, where $N_{H}$
is the number of layers for  $n_{Hi}$ and $N_L$ is the number
of layers for $n_{Li}$. Then,  $d_{Hi}$ is the monolayer
thickness of  $n_{Hi}$ at that measurement point and $d_{Li}$ is
the monolayer thickness of $n_{Hi}$ at that measurement
point. Therefore,  $d_i$ is the total thickness calculated for
each of the measurements, defining a i = $ A, B, C$. Having the
following relationship $d_i =
(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$.
Initial data for conventional design we use  $\lambda_c= 0.67 \ \
\mu m$, $n_H =2.6$, $P_H =0.46$, $d_H=0.066 \ \ \mu m
$, $t_H=35 s  $ y para  $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \ \ \mu m  $, $t_L=11 s  $. All these data are
for the point $ 0 $ which is located at one end of the sample just
below the tip counter-electrode.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MCGRIN2}
  \caption{a) Three locations at different points are
      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSMCGRIN
      sample $ GMC $. b) We have the reflectance measurements to
      know the optical properties with the proposed
      simulation. We were able to show that in a Porous Silicon
      GRIN structure, for a microcavity the data is very
      consistent with the simulation and the experiment, we
      found the refractive indices and the porosities as a
      function of the current density at each measurement point,
      see Table \ref{tabla:1}. }
  \label{fig:MCGRIN3}
\end{figure}

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    \textbf{Points} & $\lambda_c (\mu m)$ & \textbf{n} & \textbf{k} & \textbf{Porosity} & \textbf{J}$(mA/cm^2)$ & \textbf{t(s)}\\
    \hline
    A(H) & 0.65 & 2.661 & 0.0264 & 0.45 & 5.5 & 35 \\
    \hline
    B(H) & 0.58 & 2.762 & 0.0135 & 0.41 & 4.0 & 35 \\
    \hline
    C(H) & 0.54 & 2.808 & 0.0178 & 0.39 & 3.0 & 35 \\
    \hline
    A(L) & 0.65 & 1.442 & 0.0015 & 0.74 & 44 & 11 \\
    \hline
    B(L) & 0.58 & 2.295 & 0.0091 & 0.68 & 32 & 11 \\
    \hline
    C(L) & 0.54 & 2.302 & 0.001 & 0.64 & 24 & 11 \\
    \hline
  \end{tabular}
  \caption{ \emph{We have different points denoted as follows, $ A
      (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
      from the sample of a Porous Silicon Microcavity GRIN
      (PSMCGRIN) $ GMC $. Alternate layers of high refractive index
      (H) and low refractive index (L) are obtained at each of the
      measurement points (A, B and C). The refractive indexes of the
      PSMCGRIN were considered from the experimental and theoretical
      values that were obtained for the porosity ($ P =
      0.3J^{0.24}$). And we could obtain the attack time with the
      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are
considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
$ and $ C (1.2 \ \ cm) $, from the PSMCGRIN sample $ GMC $. Likewise,
Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
the optical properties with the proposed simulation. We can see how
from an experimental setup we have some important results as a result
of a whole calibration curve suitable for making GRIN porous
silicon. The refractive index of the Porous Silicon Microcavities GRIN
were considered the experimental and theoretical values obtained for
the porosity and the thicknesses shown in Table 1. The porous silicon
microcavities (MCSP) with refractive index with gradient (GRIN), were
manufactured with different current densities ranging from $ 6 \ \ mA
/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
for a $t_H=35 s $, with a high refractive index $n_H \sim$ $
2,661$ to $ 2,808$ and porosities of $P_H \sim$ $ 0.45 $ to $
0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
of $ 38 \ \ mA $, using $t_H=11 s$  for low refractive index
$n_L\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
$P_H \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
attack time could be obtained with the relation of $ V = 0.53J^{0.79}
$ where $ t = d / V $ and the refractive index using the Bruggeman
formula. For theoretical values, we use complex refractive indices as
free parameters to fit the experimental refractive spectra (Section
4.2).
 \begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
   \caption{SEM image of the cross section profile of the
       microcavities with GRIN. The measured thicknesses of the
       complete multi-film structures showed good agreement with the
       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
       ($j=H,L$), which are the thicknesses of each of the monolayer
       of the porous silicon microcavity GRIN at the measurement
       points and the total thickness we find it as $d_i =
       (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$
       defining $ i = $ A, B, C. Which resulted in (measured /
       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}
	\label{fig:MCGRIN4}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/grinJD31}
  \caption{(a) Etching rate $v$ and (b) porosity $p$ as a function of the
    density current $j_\perp$, obtained from Fig. \ref{fig:JDR}. We
    show the data points and the results of power
    law fits, yielding $v=0.53j_\perp^{0.79}$ and
    $p=0.3j_\perp^0.24$, with corresponding correlation coefficients
      $r_v^2=0.993$ and $r_p^2=0.989$ (here $v$ is in nm/s, $p$ is
      dimensionless and $j_\perp$ is in mA/cm$^2$). \notaL{cambia J por $j_\perp$, V por $v$ y P
      por $p$. Quita el letrero fitting data, la ecuación y el valor
      de $R^2$}\notaL{Los ajustes ¿son correctos con estas unidades?}}
  \label{fig:Indr1}
\end{figure}
By relating among themselves the panels of Fig. \ref{fig:JDR} we
may obtain the etching rate $v$ and the porosity $p$ as
functions of the current density $j_\perp$. The results are shown in
Fig. \ref{fig:Indr1}.\notaL{\ldots Apenas aquí dijiste cuál fue el
  tiempo de ataque de la muestra dos: relating to depth and time ($
  200 \ \ s $ ). ¿Es correcto este tiempo? Ponlo en su lugar}
We fitted the data points with simple power laws and found
\begin{equation}
  \label{eq:etch}
  v=0.53j_\perp^{0.79}
\end{equation}
and
\begin{equation}
  \label{eq:poros}
  p=0.3j_\perp^{0.24},
\end{equation}
where $v$ is
expressed in nm/s, $p$ is dimensionless and $j_\perp$ is expressed as
mA/cm$^2$. The corresponding correlation coefficients are $r_v^2=0.993$
and $r_p^2=0.989$. \notaL{Digresión teórica. El producto $pv$ es
  proporcional a la cantidad de materia removida por segundo. En mi
  opinión, esto debería ser proporcional a la corriente $pv\propto
  j_\perp$. ¿Es correcto? A tí te sale algo parecido pero no
  exacto. ¿Se podrá hacer un mejor ajuste tomando esto en cuenta?
  ¿Alguien lo ha discutido en la literatura?}\notaL{En todo caso, todo
  esto se tiene que rehacer usando la expresión teórica correcta y las
  posiciones correctas}

@@

\subsection{PS GRIN Microcavities}
\label{sec:grin-porous-silicon}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MicrGrin}
  \caption{\notaL{Está bonita la figura, pero tiene errores. La
      superficie del electrolito y la superficie de la muestra
      deben ser ambas horizontales. Cambia la fuente por fuente
      de corriente. La punta del electrodo no debe ser una
      bola. Quita todo lo que está abajo del sustrato. Mejor pon
      solamente una H en alguna región amarilla y una L en
      alguna región azul. El electrolito tiene gotas o
      burbujas. Tal vez sea mejor ponerle un color uniforme. Quita los
      anchos totales, pues no creo que nos sean útiles. Haz que los cables
      horizontales sean horizontales.}
    PS GRIN microcavity made of layers of high (H) and low (L)
    refractive index $n_H$ and $n_L$ and widths $d_H$ and $d_L$
    arranged in the sequence $(HL)_NHH(HL)_N$. Both the index of
    refraction and the widths depend on position along the
    sample and are chosen to obey a quarter wavelength
    condition at a given position $A$ and wavelength $\lambda_c$.
  }
  \label{fig:MCGRIN0}
\end{figure}

As a simple application of our preparation and calibration methods, we
prepare a PS GRIN microcavity (MC), as illustrated in
Fig. \ref{fig:MCGRIN0}.  Alternate layers of relatively high (H) and low and low
(L) refractive indices $n_H$ and $n_L$, of corresponding thicknesses
$d_H$ and $d_L$, are prepared by alternatingly etching a Si sample in our
electrolytic cell with a current $I_H$ during a time $t_H$ and with a
current $I_L$ during a time $t_L$. We chose the currents $I_H=5\text{mA}$
and $I_L=40\text{mA}$ \notaL{¿son correctos estos valores?}, the same
that were used above to prepare samples $G_1$ and $G_2$.
We chose the etching times to obtain a MC at the given
position $A$ tuned to a given wavelength
$\lambda_c=0.67\mu\text{m}$. Thus, we chose the thicknesses so they
correspond to quarter wavelength plates, $n_Hd_H=n_Ld_L=\lambda_c/4$,
at this position and wavelength, yielding $n_H =2.6$,\notaL{Por qué no
  coincide con el dato de la tabla 1?} $p_H =0.46$,
$d_H=0.066\mu\text{m}$, $t_H=35\text{s}$, $n_L= 1.4$, $p_L =0.75$,
$d_L=0.117\mu\text{m}$, $t_L=11\text{s}$.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MCGRIN2}
  \caption{(a)Top view photograph of a PS GRIN MC showing the position
    of the three measuring points $A$, $B$ and $C$. The cavity was
    tuned to the wavelength $\lambda_c=0.67\mu\text{m}$ at position
    $A$ (see text). We chose $x_A=0.3\text{cm}$, $x_B=0.8\text{cm}$,
    and $x_C=1.2\text{cm}$. (b-d) Reflectance spectra measured and
    calculated at positions $A-C$. For the calculation, the porosity
    and etching rates were obtained from Fig. \ref{fig:Indr1},
    the dielectric functions and indices of refracton from
    Eqs. \eqref{Eq:Brugg} and the reflectance from standard transfer
    matrix theory. \notaL{Quizás haya que usar D E F en lugar de A B
      C, pues A B C se usó para otras posiciones sobre la muestra
      $G_1$ y $G_2$. ¿Son correctas las posiciones aquí?}}
  \label{fig:MCGRIN3}
\end{figure}

\begin{table}
  \begin{tabular}{ccccccc}
    \hline
    Pos(kind)&Current(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
    \hline
    \hline
    A(H) & 5.5 & 0.45& 2.66& 0.65   \\
    A(L) & 44  & 0.74& 1.44& 0.65   \\
    B(H) & 4.0 & 0.41& 2.76& 0.58   \\
    B(L) & 32  & 0.68& 2.29& 0.58   \\
    C(H) & 3.0 & 0.39& 2.81&0.54    \\
    C(L) & 24  & 0.64& 2.30&0.54    \\
  \end{tabular}
  \caption{Some properties of the PS GRIN MC corresponding to the
    positions $A$, $B$ and $C$ and the corresponding high ($H$) and
    low ($L$) index layers. The current densities were obtained by
    scaling the results in Fig. \ref{fig:DR1} with $I_H$ and
    $I_L$, the depths were obtained from the etching
    times and the current density using \eqref{eq:etch}, the porosity
    was obtained from Eq. \eqref{eq:poros}, the indices of refraction
    were obtained from Eq. \eqref{Eq:Brugg} using the porosity, and
    the resonant wavelengths of the cavity were read from
    Fig. \ref{fig:MCGRIN3}.
    \notaL{Inventé lo de arriba. Qué es cierto y qué
      mentira?}\notaL{Por qué resuenas en 0.65 si habías diseñado
      0.67 en A?} \notaL{¿De dónde sacaste
        $\lambda_c$ para los otros puntos? ¿Cómo le hiciste para que
        $\lambda_c$ diera lo mismo en $H$ y en $L$? $n$ y $k$ dependen de la
        frecuencia. ¿Qué frecuencia usaste para darles valores en esta
        tabla?}\notaL{quité digitos a n. quité k pues es chiquita,
        ¿no? quité los tiempos pues son los mismos. Quité las
        posiciones pues están descritas antes. Añade una columna
        con las profundidades $d_H$ y $d_L$. }}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} we show a photograph of a PS GRIN MC
sample, which displays a color that shifts towards the blue when we
move towards its right, that is, away from where the electrode was
positioned. In the figure we indicate three points with $x$ coordinate
$x_A=0.3\text{cm)$ , $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$.
  \notaL{***Aquí voy***}
  Likewise,
Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
the optical properties with the proposed simulation. We can see how
from an experimental setup we have some important results as a result
of a whole calibration curve suitable for making GRIN porous
silicon. The refractive index of the Porous Silicon Microcavities GRIN
were considered the experimental and theoretical values obtained for
the porosity and the thicknesses shown in Table 1. The porous silicon
microcavities (MCSP) with refractive index with gradient (GRIN), were
manufactured with different current densities ranging from $ 6 \ \ mA
/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
for a $t_H=35 s $, with a high refractive index $n_H \sim$ $
2,661$ to $ 2,808$ and porosities of $P_H \sim$ $ 0.45 $ to $
0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
of $ 38 \ \ mA $, using $t_H=11 s$  for low refractive index
$n_L\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
$P_H \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
attack time could be obtained with the relation of $ V = 0.53J^{0.79}
$ where $ t = d / V $ and the refractive index using the Bruggeman
formula. For theoretical values, we use complex refractive indices as
free parameters to fit the experimental refractive spectra (Section
4.2).
   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
   \caption{SEM image of the cross section profile of the
       microcavities with GRIN. The measured thicknesses of the
       complete multi-film structures showed good agreement with the
       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
       ($j=H,L$), which are the thicknesses of each of the monolayer
       of the porous silicon microcavity GRIN at the measurement
       points and the total thickness we find it as $d_i =
       (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$
       defining $ i = $ A, B, C. Which resulted in (measured /
       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}
	\label{fig:MCGRIN4}
